---
title: "R Notebook"
output: html_notebook
---

```A brief introduction to the dataset```

This data set has cake ingredients of some cakes and a table of ingredient
codes. 

```A list of any assumptions you have made```
For question 4 I assumed that it asked for the highest amount of types of 
ingredients used in a cake.

Soure cream cup I assumed that it's measured in cups 

```The steps you took to clean the data (you don’t need to write out in detail every step, but a combination of commented code chunks with surrounding overall explanations would be great).```
I put all the ingredient code together as one column. 
```{r}
cake <- cake %>% 
  pivot_longer(cols = c(2:35), 
               names_to = "ing_code",
               values_to = "amount")
```
I joined the cake table with the code table, I kept the code as well as the name 
of the ingredients. They might be useful for different things. 
```{r}
cake <- cake %>% 
  left_join(ingredient, by = c("ing_code" = "code")) %>% 
  relocate(amount, .after = measure)
```
I fixed the NA in measure, I assumed that the unit is cup. 
```{r}
ingredient <- ingredient %>% 
  mutate(measure = case_when(ingredient == 'Sour cream cup' ~ 'cup',
                            TRUE ~ measure))
```

I cleaned the names here and put the strings to lower case.
```{r}
cake <- cake %>% 
  clean_names() %>% 
  mutate(across(where(is.character), ~str_to_lower(.x))) %>% 
  drop_na(amount)
```


```The answers to the questions presented in the task brief```
_Which cake has the most cocoa in it?_
#Only two cakes has Cocoa, others are all NA.
#One Bowl Chocolate has 10 tablespoons 

_For sponge cake, how many cups of ingredients are used in total?_
#I don't understand what the question is asking. 
#My first codes count how many ingredients uses cup as unit 
--3 cups
#Second codes add up all the cups.
--3.5 cups 
#I think the second code if more like a coding question but doesn't seem
to make sense in real life.

_How many ingredients are measured in teaspoons?_
#8 ingredients use teaspoon as unit 

_Which cake has the most unique ingredients?_
My understanding to this question is : which cake has the highest
amount of ingredients used. I took unique as different not special. 
#babas au rhum  and one bowl chocolate have the most amount, 11.

_Which ingredients are used only once?_
#the following 8 ingredients are only used once
#bananas				
#cream of tartar				
#crushed ice				
#dried currants				
#egg white				
#nutmeg				
#nuts				
#zwiebach

```Any other interesting analyses or conclusions you come across.```
buche de noel	is the most simple cake to make it only needs 5 ingredients 	