---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
library(tidyr)
library(here)
candy <- read_csv(here("clean_data/clean_candy"))
```

What is the total number of candy ratings given across the three years. (Number of candy ratings, not the number of raters. Don’t count missing values)
```{r}
candy %>% 
  select(emotion) %>% 
  drop_na(emotion) %>% 
  summarise (num = n())
 #772352 ratings were giving out throughout the three years. 
```

What was the average age of people who are going out trick or treating?
```{r}
candy %>% 
  filter(going_out == 'Yes') %>%
  summarise(avg_age = round(mean(age, na.rm= TRUE)))
#35?????ummmmmmmm very strange. But I kept all the age between 0 to 119. 
```

What was the average age of people who are not going trick or treating?
```{r}
candy %>% 
  filter(going_out == 'No') %>%
  summarise(avg_age = round(mean(age, na.rm= TRUE)))
#39 average age 
```

For each of joy, despair and meh, which candy bar received the most of these ratings?
```{r}
candy %>% 
  drop_na(emotion, sweets) %>% 
  group_by(emotion, sweets) %>% 
  summarise(count = n()) %>% 
  slice_max(count)

#Mary Janes is most-DESPAIR	with count 10677
#Regular M&M is most-joy with count	11138
#Regular M&M	is most - MEH with count 4309
```

How many people rated Starburst as despair?
```{r}
candy %>% 
  filter(sweets == 'Starburst' ,
         emotion == 'DESPAIR') %>% 
  summarise(total_n = n())
#1990 in total across 3 years.
```

For the next three questions, count despair as -1, joy as +1, and meh as 0.


```{r}
candy_rate <- candy %>% 
  mutate(rating = case_when(emotion == 'JOY' ~ 1,
                            emotion == 'DESPAIR' ~ -1,
                            emotion == 'MEH' ~ 0,
                            TRUE ~ NA_real_))
```

What was the most popular candy bar by this rating system for each gender in the dataset ?
```{r}
candy_rate %>% 
  select(sweets, rating, gender) %>% 
  drop_na(gender) %>% 
  group_by(gender, sweets) %>% 
  summarise(points = sum(rating, na.rm = TRUE)) %>% 
  slice_max(points)

#It's all regular M&M.. I did put all the M&M together.... 
#2064 votes in Female,
#176 for I'd rather not say
#3485 for male
#other 86
```

What was the most popular candy bar in each year?
```{r}
candy_rate %>% 
  select(timestamp, sweets, rating) %>% 
  group_by(timestamp, sweets) %>% 
  summarise(points = sum(rating, na.rm = TRUE)) %>% 
  slice_max(points)
#any full-size candy bar for 2015 4603 votes
#regular M&M for 2016 and 2017 with 1705 and 4150 votes
```

What was the most popular candy bar by this rating for people in US, Canada, UK, and all other countries?
```{r}
candy_rate %>% 
  select(country, sweets, rating) %>% 
  drop_na(country) %>% 
  mutate(country = recode(country, 'US' = 'US',
                          'UK' = 'UK',
                          'Canada' = 'Canada',
                          .default = 'other')) %>% 
  group_by(country, sweets) %>% 
  summarise(points = sum(rating, na.rm = TRUE)) %>% 
  slice_max(points)
#M&M again..... Canada 600, other 114, UK 91 and US 4939
```

